---
title: "age_group"
author: "Shuya Liu"
date: "December 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

Data Import
---

```{r data}
## read datasets
happy_data <- read_excel("./data/Chapter2OnlineData.xls") %>%
  janitor::clean_names()
age_data <- read_excel("./data/GallupAnalytics_Export_20191203_075046.xlsx",
                       range = "B8:G5209") %>%
  janitor::clean_names() %>%
  rename(country_name = geography,
         year = time,
         age = demographic_value,
         n = n_size,
         ladder = value) %>%
  mutate(year = as.numeric(year))

## join datasets
age_df <- age_data %>%
  pivot_wider(names_from = age,
              values_from = c(ladder, n)) %>%
  left_join(happy_data, ., by = c("country_name", "year")) %>%
  select(country_name:life_ladder, "ladder_15-29":"n_DK/Refused") %>%
  pivot_longer("ladder_15-29":"n_DK/Refused", 
               names_to = c("variable", "age"),
               names_pattern = "(.*)_(.*)") %>%
  pivot_wider(names_from = variable,
              values_from = value)

```


Boxplot of Age Groups
---
```{r boxplot}
age_df %>%
  filter(age != "DK/Refused") %>%
  drop_na %>%
  mutate(age = as.factor(age)) %>%
  ggplot(aes(x = age, y = ladder, color = age)) +
  geom_boxplot() +
  labs(
    title = "The Boxplot of Happiness Score",
    x = "Year",
    y = "Happiness Score"
  ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.95, vjust = 0.2)) +
  facet_grid(~year)
```

Analysis
---
By plotting the boxplots throughout the years, we can see that overall there are distinct differences among these age groups. It is relatively obvious that the age group of `15-29` have rank their happiness in higher scores than the other two groups, and the age group of `50+` tend to have the lowest happiness score . It appears that younger people tend to have higher happiness score, ie. the `life_ladder` variable. Therefore, we are going to include `age_group` as one of the factor in our final regression model since the strong association we see in this graph.

Additional Link
---
The happiness score for each age groups of different countries throughout the years can be found on [this](https://lsyjessica.shinyapps.io/shiny_dashboard_template/) shiny dashboard.

